---
title: "Scatterplot and Linear correlation Ghana Sorting Data"
author: "Ruben"
date: "September 23, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("C:/Users/ruben/Desktop/Rstudio")

library(tidyverse)
library(ggplot2)
library(ggpubr)
library(reshape2)
```

```{r}
Ghana <- read.csv("Ghana_sorted_toxinFM.csv", header = TRUE)

#create 1 to 1 line for graphs

line_ratio <- read.csv("1_to_1_lines.csv", header = TRUE)


```




#Linear scatterplot Reject and Bulk

```{r}
eval = FALSE

lm(data=Ghana, formula = AF_ppb_reject~AF_ppb_bulk)

LM_reject_bulk <- lm(Ghana$AF_ppb_reject~Ghana$AF_ppb_bulk)

summary(LM_reject_bulk)

summary(LM_reject_bulk)$coefficients[,4]

LM_reject_bulk$coefficients[[1]]

lmp <- function (modelobject) {
    if (class(modelobject) != "lm") stop("Not an object of class 'lm' ")
    f <- summary(modelobject)$fstatistic
    p <- pf(f[1],f[2],f[3],lower.tail=F)
    attributes(p) <- NULL
    return(p)
}

lmp(LM_reject_bulk)


Ghana_linear_reject_bulk <- ggplot(data = Ghana, aes(AF_ppb_bulk, y=AF_ppb_reject)) + 
geom_point() +
geom_smooth(method=lm) + 
scale_x_continuous("Bulk Aflatoxin Level (ppb)") + 
scale_y_continuous("Reject Aflatoxin Level (ppb)")+ 
geom_abline(intercept = 0, slope = 1, lty=2) + 
coord_cartesian(ylim = c(0, 80), xlim = c(0, 65)) + 
ggtitle("Aflatoxin") + 
geom_label(aes(x = 55, y = 75), hjust = 0, 
             label = paste(
                                          "Intercept =",signif(LM_reject_bulk$coefficients[[1]],3 ),
                                               " \nSlope =",signif(LM_reject_bulk$coefficients[[2]], 3),
                                               " \nP =",signif(lmp(LM_reject_bulk), 3)))

plot(Ghana_linear_reject_bulk)

#Correlate the 2 data points. The correlation coefficient is a number between 1 and -1, The magnitude of the number indicates the strength of the linear relationship. The sign corresponds to the direction of that relationship. A correlation coefficient of -1 indicates a near perfect negatively correlated linear relationship.

cor(Ghana$AF_ppb_bulk, Ghana$AF_ppb_reject)

```

# For figure run from here!


```{r}


Plot_creation<-function(col1s, col2s, title, xtitle, ytitle, xposition, yposition,xmax, ymax, xmin, ymin){
  

  col1mod <- Ghana[[col1s]]
  col2mod<-Ghana[[col2s]]
  
  LM_reject_bulk <- lm(formula = col2mod~col1mod)
  
  summary(LM_reject_bulk)
  
  summary(LM_reject_bulk)$coefficients[,4]
  
  LM_reject_bulk$coefficients[[1]]
  
  lmp <- function (modelobject) {
      if (class(modelobject) != "lm") stop("Not an object of class 'lm' ")
      f <- summary(modelobject)$fstatistic
      p <- pf(f[1],f[2],f[3],lower.tail=F)
      attributes(p) <- NULL
      return(p)
  }
  
  lmp(LM_reject_bulk)
  
  
  Ghana_linear_reject_bulk <- ggplot(data = Ghana, aes_string(x=col1s, y=col2s)) + 
  geom_point(size = 0.9) +
  geom_smooth(method=lm) + 
  scale_x_continuous(xtitle) + 
  scale_y_continuous(ytitle)+ 
  coord_cartesian(ylim = c(ymin, ymax), xlim = c(xmin, xmax)) + 
  ggtitle(title) + 
  geom_label(aes(x = xposition, y = yposition), size = 2.80 ,hjust = 0, 
               label = paste(
                                                 "Intercept =",signif(LM_reject_bulk$coefficients[[1]],3 ),
                                                 " \nSlope =",signif(LM_reject_bulk$coefficients[[2]], 3),
                                                 " \nP =",signif(lmp(LM_reject_bulk), 3))) 
  
  plot(Ghana_linear_reject_bulk)
  return(Ghana_linear_reject_bulk)
    
}
```

# LM Reject and Bulk

```{r}
GhanaAF_reject_bulk  <- Plot_creation(col1s ="AF_ppb_bulk" , 
               col2s = "AF_ppb_reject",
              title = "Aflatoxin", 
              xtitle = "Bulk Aflatoxin Level (ppb)",
              ytitle = "Reject Aflatoxin (ppb)",
              xposition = 54,
              yposition = 68,
              xmax = 70,
              ymax = 80,
              xmin = 0,
              ymin = 0
              ) + geom_abline(intercept = 0, slope = 1, lty=2) + theme(text = element_text(size = 10))

AF2 <- plot(GhanaAF_reject_bulk)

```
# LM accept and Bulk

```{r}
GhanaAF_accept_bulk  <- Plot_creation(col1s ="AF_ppb_bulk" , 
               col2s = "AF_ppb_accept",
              title = "Aflatoxin", 
              xtitle = "Bulk Aflatoxin Level (ppb)",
              ytitle = "Accept Aflatoxin (ppb)",
              xposition = 54,
              yposition = 68,
              xmax = 70,
              ymax = 80,
              xmin = 0,
              ymin = 0
              ) + geom_abline(intercept = 0, slope = 1, lty=2) + theme(text = element_text(size = 10))


AF1 <- plot(GhanaAF_accept_bulk)

```



# LM Diference (accept-reject) and Bulk


```{r}
GhanaAF_dif_bulk  <- Plot_creation(col1s = "AF_ppb_bulk", 
               col2s = "Diference_accept_reject_AF",
              title = "Aflatoxin", 
              xtitle = "Bulk Aflatoxin Level (ppb)",
              ytitle = "Difference Aflatoxin Accept-Reject (ppb)",
              xposition = 54,
              yposition = 3.2,
              xmax = 70,
              ymax = 10,
              xmin = 0,
              ymin = -80
              )  + geom_hline(yintercept=0, linetype="dashed", color = "tomato2") + theme(text = element_text(size = 10))


AF3 <- plot(GhanaAF_dif_bulk)

```


#LM Reject and bulk FM

```{r}

GhanaFM_reject_bulk  <- Plot_creation(col1s ="FM_ppm_bulk" , 
               col2s = "FM_ppm_reject",
              title = "Fumonisin", 
              xtitle = "Bulk Fumonisin Level (ppm)",
              ytitle = "Reject Fumonisin (ppm)",
              xposition = 4.6,
              yposition = 7.25,
              xmax = 6,
              ymax = 8,
              xmin = 0,
              ymin = 0
              ) + geom_abline(intercept = 0, slope = 1, lty=2) + theme(text = element_text(size = 10))


FM2 <- plot(GhanaFM_reject_bulk)


```


#LM Accept and bulk FM

```{r}

GhanaFM_accept_bulk  <- Plot_creation(col1s ="FM_ppm_bulk" , 
               col2s = "FM_ppm_accept",
              title = "Fumonisin", 
              xtitle = "Bulk Fumonisin Level (ppm)",
              ytitle = "Accept Fumonisin (ppm)",
              xposition = 4.6,
              yposition = 7.25,
              xmax = 6,
              ymax = 8,
              xmin = 0,
              ymin = 0
              ) + geom_abline(intercept = 0, slope = 1, lty=2) + theme(text = element_text(size = 10))


FM1 <- plot(GhanaFM_accept_bulk)


```

#LM Diference (accept-reject) and bulk FM

```{r}
GhanaFM_dif_bulk  <- Plot_creation(col1s = "FM_ppm_bulk", 
               col2s = "Diference_accept_reject_FM",
              title = "Fumonisin", 
              xtitle = "Bulk Fumonisin Level (ppm)",
              ytitle = "Difference Fumonisin Accept-Reject (ppm)",
              xposition = 4.6,
              yposition = -1,
              xmax = 6,
              ymax = 0,
              xmin = 0,
              ymin = -8
              )  + geom_hline(yintercept=0, linetype="dashed", color = "tomato2") + theme(text = element_text(size = 10))  


FM3 <- plot(GhanaFM_dif_bulk)
```


# Create Figure 4

```{r}

Fig4 <- ggarrange(AF1, FM1, AF2, FM2, AF3, FM3,
          ncol = 2, nrow = 3)

Fig4
```



# FIG. 5 LM Mass percentage reject and Fraction Reject

```{r}
GhanaAF_mass_toxin  <- Plot_creation(col1s ="Reject_mass_perc" , 
               col2s = "Fraction_reject_AF",
              title = "Aflatoxin", 
              xtitle = "Percent of Mass reject (%)",
              ytitle = "Percent Aflatoxin removed (%)",
              xposition = 0.28,
              yposition = 0.15,
              xmax = 0.4,
              ymax = 1.00,
              xmin = 0,
              ymin = 0
              ) + geom_abline(intercept = 0, slope = 1, lty=2) + theme(text = element_text(size = 10)) 


AF1.1 <- plot(GhanaAF_mass_toxin)

```

# FIG. 5 LM Mass percentage reject and Fraction Reject

```{r}
GhanaAF_mass_bulk  <- Plot_creation(col1s ="AF_ppb_bulk" , 
               col2s = "Weight_reject",
              title = "Aflatoxin", 
              xtitle = "Bulk Aflatoxin Level (ppb)",
              ytitle = "Mass Removed (g)",
              xposition = 53,
              yposition = 40,
              xmax = 70,
              ymax = 60,
              xmin = 0,
              ymin = 0
              )  + theme(text = element_text(size = 10)) 


AF2.1 <- plot(GhanaAF_mass_bulk)

```
# FIG. 5 LM Mass percentage reject and Fraction Reject FM

```{r}
GhanaFM_mass_toxin  <- Plot_creation(col1s ="Reject_mass_perc" , 
               col2s = "Fraction_reject_FM",
              title = "Fumonisin", 
              xtitle = "Percent of Mass reject (%)",
              ytitle = "Percent Fumonisin removed (%)",
              xposition = 0.28,
              yposition = 0.15,
              xmax = 0.4,
              ymax = 1.00,
              xmin = 0,
              ymin = 0
              ) + geom_abline(intercept = 0, slope = 1, lty=2) + theme(text = element_text(size = 10)) 


FM1.1 <- plot(GhanaFM_mass_toxin)

```

# FIG. 5 LM Mass percentage reject and Fraction Reject FM

```{r}
GhanaFM_mass_bulk  <- Plot_creation(col1s ="FM_ppm_bulk" , 
               col2s = "Weight_reject",
              title = "Fumonisin", 
              xtitle = "Bulk Fumonisin Level (ppm)",
              ytitle = "Mass Removed (g)",
              xposition = 4.3,
              yposition = 40,
              xmax = 6,
              ymax = 60,
              xmin = 0,
              ymin = 0
              )  + theme(text = element_text(size = 10)) 


FM2.1 <- plot(GhanaFM_mass_bulk)

```

#Create Figure 5

```{r}

Fig5 <- ggarrange(AF1.1, FM1.1, AF2.1, FM2.1,
          ncol = 2, nrow = 2)

Fig5

```


#Boxplot mass percentage sorted and percetange of toxin reduced

```{r}
Ghana2 <- read.csv("Ghana_sorted_AF_1_masstest2.csv", header = TRUE)

AFfarmsweight <- ggplot(data = Ghana2) + 
  geom_boxplot(aes(x= Sample_type, y= perc_weight2 )) + labs(title = "Percentage of Sample Mass in Accept and Reject Stream after Sorting", x = "Sorted Sample", y = "Mass Sorted (%)") + theme(legend.position = c(0.2, 0.8)) + coord_cartesian(ylim = c(0, 1)) + theme(text = element_text(size = 10))

#+ annotate("text", x = 0.6, y = 3, label = paste ("Mean ==", mean_d1), parse = TRUE) + annotate("text", x = 0.6, y = 2.8, label = paste ("Mode ==", mode_d1), parse = TRUE)


MS <- plot (AFfarmsweight)

```


```{r}
Ghana3 <- read.csv("Toxin_percentage_removal_ghana.csv", header = TRUE)

AFfarmstoxinremoval <- ggplot(data = Ghana3) + 
  geom_boxplot(aes(x= Sample_type, y= Perc_toxin_removed_AF)) + labs(title = "Percentage of Total Aflatoxin Fraction Removed by Sorting", x = "Sample Stream", y = "Aflatoxin removed in Reject Samples (%)") + theme(legend.position = c(0.2, 0.8)) + coord_cartesian(ylim = c(0, 1)) + theme(text = element_text(size = 10))

#+ annotate("text", x = 0.6, y = 3, label = paste ("Mean ==", mean_d1), parse = TRUE) + annotate("text", x = 0.6, y = 2.8, label = paste ("Mode ==", mode_d1), parse = TRUE)


MSAF <- plot (AFfarmstoxinremoval)
```


```{r}
Ghana4 <- read.csv("Toxin_percentage_removal_ghana_FM.csv", header = TRUE)

FMfarmstoxinremoval <- ggplot(data = Ghana4) + 
  geom_boxplot(aes(x= Sample_type, y= Perc_toxin_removed_FM)) + labs(title = "Percentage of Total Fumonisin Fraction Removed by Sorting", x = "Sample Stream", y = "Fumonisin removed in Reject Samples (%)") + theme(legend.position = c(0.2, 0.8)) + coord_cartesian(ylim = c(0, 1)) + theme(text = element_text(size = 10))

#+ annotate("text", x = 0.6, y = 3, label = paste ("Mean ==", mean_d1), parse = TRUE) + annotate("text", x = 0.6, y = 2.8, label = paste ("Mode ==", mode_d1), parse = TRUE)


MSFM <- plot (FMfarmstoxinremoval)
```

#Make FIgure 3

```{r}

Fig3 <- ggarrange(MS, MSAF, MSFM, nrow = 1)

Fig3

```






