---
title: "FM Data Analysis Ghana Sorting"
author: "Ruben"
date: "October 4, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("C:/Users/ruben/Desktop/Rstudio")

library(tidyverse)
library(ggplot2)

library(reshape2)
library(gridExtra)
library(data.table)
library(patchwork)
library(ggpubr)
library(grid)
library(ragg)
```

#Load Files

```{r}
GhanaFM <- read.csv("Ghana_sorted_toxinFM.csv", header = TRUE)

```

#Graph Reduction Accept and Reject FM

```{r}
data1 <- data.frame (x= GhanaFM$Sample_ID, y1 = GhanaFM$FM_ppm_accept, y2 = GhanaFM$FM_ppm_reject)


datalist<-data1$x
print(datalist)


data_long1 <- melt(data1, id = "x")

head(data_long1)



ggp1FM <- ggplot(data_long1,  aes(x = factor(x, level = datalist), y = value, color = variable, shape = variable, show.legend = F))+  geom_point() + geom_line(aes(group = x), color = "black",arrow = arrow(length=unit(0.1,"cm"), ends="first", type = "closed")) +  labs(x = "Sample ID", y = "Fumonisin Level (ppm)", fill = "Fumonisin Type" ) + scale_color_manual( values = c("blue", "red"), name = "Sorting Results",labels = c( "Accept Stream", "Reject Stream")) + theme(axis.text.x = element_text(vjust = 0.5,angle = 90), text = element_text(size = 11), legend.position = c(0.85, 0.8)) + scale_shape_manual(values = c(16,17,4), name = "Sorting Results",labels = c( "Accept Stream", "Reject Stream")) + geom_hline(yintercept=2,  linetype="dashed", color = "tomato2") + ggtitle("Fumonisin levels of rejected and accepted streams after sorting") + coord_cartesian(ylim = c(0, 7)) + theme(text = element_text(size = 10))

ggp1FM
```

#Graph Accept, Reject and Bulk

```{r}
data2 <- data.frame (x= GhanaFM$Sample_ID, y1 = GhanaFM$FM_ppm_accept, y2 = GhanaFM$FM_ppm_reject, y3= GhanaFM$FM_ppm_bulk)


datalist2<-data2$x
print(datalist2)

data_long2 <- melt(data2, id = "x")

head(data_long2)



ggp2FM <- ggplot(data_long2,  aes(x = factor(x, level = datalist2), y = value, color = variable, shape = variable, show.legend = F))+  geom_point() +  labs(x = "Sample ID", y = "Fumonisin Level (ppm)", fill = "Fumonisin Type" ) + scale_color_manual( values = c("blue", "red","black"), name = "Sorting Results",labels = c( "Accept Stream", "Reject Stream", "Bulk Level")) + theme(axis.text.x = element_text(vjust = 0.5,angle = 90), text = element_text(size = 11), legend.position = c(0.85, 0.8)) + scale_shape_manual(values = c(16,17,2), name = "Sorting Results",labels = c( "Accept Stream", "Reject Stream", "Bulk Level")) + geom_hline(yintercept=2, linetype="dashed", color = "tomato2") + ggtitle("Fumonisin levels of rejected and accepted streams after sorting") + coord_cartesian(ylim = c(0, 7)) + theme(text = element_text(size = 10))

ggp2FM




```


```{r}
Ghana <- read.csv("Ghana_sorted_toxinAF.csv", header = TRUE)


```


```{r}
data1AF <- data.frame (x= Ghana$Sample_ID, y1 = Ghana$AF_ppb_accept, y2 = Ghana$AF_ppb_reject)


datalistAF<-data1AF$x
print(datalistAF)

#setDT(data1)


data_long1AF <- melt(data1AF, id = "x")


#data_long1 <- data1 %>% mutate (direction = ifelse(y2 - y1 > 0 , "up", "Down")) %>%  melt(id = c( "x", "direction"))

head(data_long1AF)



ggp1AF <- ggplot(data_long1AF, aes(x = factor(x, level = datalistAF), y = value, color = variable, shape = variable, show.legend = F, group = "x")) +  geom_point() + geom_line(aes(group = x), color = "black",arrow = arrow(length=unit(0.1,"cm"), ends="first", type = "closed")) +  labs(x = "Sample ID", y = "Aflatoxin Level (ppb)", fill = "Aflatoxin Type" ) + scale_color_manual( values = c("blue", "red"), name = "Sorting Results",labels = c( "Accept Stream", "Reject Stream")) + theme(axis.text.x = element_text(vjust = 0.5,angle = 90), text = element_text(size = 11), legend.position = c(0.85, 0.8)) + scale_shape_manual(values = c(17,4), name = "Sorting Results",labels = c( "Accept Stream", "Reject Stream"))+ geom_hline(yintercept=15, linetype="dashed", color = "tomato2") + coord_cartesian(ylim = c(0, 80))  + ggtitle("Aflatoxin levels of rejected and accepted streams after sorting") + theme(text = element_text(size = 10))

#g1 <- ggplot(data_long1, aes(x=factor(x, level = datalist), y = value, color = variable, group = x )) + geom_point(size=4) + geom_path(aes(color = direction), arrow=arrow()) + labs(x = "Sample ID", y = "Aflaotxin Level (ppb)", fill = "Aflatoxin Type" )  + scale_shape_manual(values = c(17,4), name = "Aflatoxin Measurement",labels = c( "Accept Stream", "Reject Stream"))

ggp1AF

#g1


# bulk, reject, accept levels, no arrows
data2AF <- data.frame (x= Ghana$Sample_ID, y1 = Ghana$AF_ppb_accept, y2 = Ghana$AF_ppb_reject, y3= Ghana$AF_ppb_bulk)


datalist2AF<-data2AF$x
print(datalist2AF)

#setDT(data1)


data_long2AF <- melt(data2AF, id = "x")


#data_long1 <- data1 %>% mutate (direction = ifelse(y2 - y1 > 0 , "up", "Down")) %>%  melt(id = c( "x", "direction"))

head(data_long2AF)



ggp2AF <- ggplot(data_long2AF, aes(x = factor(x, level = datalist2AF), y = value, color = variable, shape = variable, show.legend = F, group = "x")) +  geom_point()  +  labs(x = "Sample ID", y = "Aflatoxin Level (ppb)", fill = "Aflatoxin Type" ) + scale_color_manual( values = c("blue", "red","black"), name = "Sorting Results",labels = c( "Accept Stream", "Reject Stream","Bulk Level")) + theme(axis.text.x = element_text(vjust = 0.5,angle = 90), text = element_text(size = 11), legend.position = c(0.85, 0.8)) + scale_shape_manual(values = c(17,4,2), name = "Sorting Results",labels = c( "Accept Stream", "Reject Stream","Bulk Level"))+ geom_hline(yintercept=15, linetype="dashed", color = "tomato2") + ggtitle("Aflatoxin levels of rejected and accepted streams after sorting") + coord_cartesian(ylim = c(0, 80))+ theme(text = element_text(size = 10)) 

#g1 <- ggplot(data_long1, aes(x=factor(x, level = datalist), y = value, color = variable, group = x )) + geom_point(size=4) + geom_path(aes(color = direction), arrow=arrow()) + labs(x = "Sample ID", y = "Aflaotxin Level (ppb)", fill = "Aflatoxin Type" )  + scale_shape_manual(values = c(17,4), name = "Aflatoxin Measurement",labels = c( "Accept Stream", "Reject Stream"))

ggp2AF




```

#Make Figure 2 and S2

```{r}

Fig2 <- ggarrange(ggp1AF, ggp1FM, common.legend = FALSE,
          nrow = 2)

Fig2

FigS2 <- ggarrange(ggp2AF, ggp2FM, common.legend = FALSE,
          ncol = 1, nrow = 2)

FigS2

```


#Linear Coreletation bulk and accept

```{r}
GhanaFM_linear_accept_bulk <- ggplot(data = GhanaFM, aes(FM_ppm_bulk, y=FM_ppm_accept)) + geom_point() + geom_smooth(method=lm) + geom_abline(intercept = 0, slope = 1, lty=2)  + scale_y_continuous("Accept Fumonisin Level (ppm)", limits=c(0,1)) +  ggtitle("Fumonisin") + stat_regline_equation(label.x=4, label.y=0.6) 

#ggplot(data = GhanaFM, aes(FM_ppm_bulk, y=Diference_accept_reject_FM)) + geom_point() + geom_smooth(method=lm) + scale_x_continuous("Bulk Fumonisin Level (ppm)") + scale_y_continuous("Diference Accept-Reject") + geom_hline(yintercept=0, linetype="dashed", color = "tomato2") + ggtitle("Fumonisin")


#+ scale_y_continuous("Accept Fumonisin Level (ppm)") + geom_abline(intercept = 0, slope = 1, lty=2) + coord_cartesian(xlim = c(0, 6), ylim = c(0,0.7) ) + ggtitle("Fumonisin") + geom_ribbon(aes(ymin= lowerbound, ymax=upperbound, fill="blue"))


plot(GhanaFM_linear_accept_bulk)

#Correlate the 2 data points. The correlation coefficient is a number between 1 and -1, The magnitude of the number indicates the strength of the linear relationship. The sign corresponds to the direction of that relationship. A correlation coefficient of -1 indicates a near perfect negatively correlated linear relationship.

cor(GhanaFM$FM_ppm_bulk, GhanaFM$AF_ppb_accept)


#Linear Model to see if prediction is statistically significant

LM_accept_bulk_FM <- lm(GhanaFM$AF_ppb_accept ~ GhanaFM$FM_ppm_bulk)

summary(LM_accept_bulk_FM)


```


#Linear Coreletation bulk and Reject

```{r}
GhanaFM_linear_reject_bulk <- ggplot(data = GhanaFM, aes(FM_ppm_bulk, y=FM_ppm_reject)) + geom_point() + geom_smooth(method=lm, se=TRUE) + scale_x_continuous("Bulk Fumonisin Level (ppm)") + scale_y_continuous("Reject Fumonisin Level (ppm)") + geom_abline(intercept = 0, slope = 1, lty=2) + ggtitle("Fumonisin") + stat_regline_equation(label.x=4, label.y=2) 

plot(GhanaFM_linear_reject_bulk)

#Correlate the 2 data points. The correlation coefficient is a number between 1 and -1, The magnitude of the number indicates the strength of the linear relationship. The sign corresponds to the direction of that relationship. A correlation coefficient of -1 indicates a near perfect negatively correlated linear relationship.

cor(GhanaFM$FM_ppm_bulk, GhanaFM$AF_ppb_reject)


#Linear Model to see if prediction is statistically significant

LM_reject_bulk_FM <- lm(GhanaFM$AF_ppb_reject ~ GhanaFM$FM_ppm_bulk)

summary(LM_reject_bulk_FM)


```
#Linear Coreletation bulk and Difference Accept-Reject

```{r}
GhanaFM_linear_dif_bulk <- ggplot(data = GhanaFM, aes(FM_ppm_bulk, y=Diference_accept_reject_FM)) + geom_point() + geom_smooth(method=lm) + scale_x_continuous("Bulk Fumonisin Level (ppm)") + scale_y_continuous("Diference Accept-Reject") + geom_hline(yintercept=0, linetype="dashed", color = "tomato2") + ggtitle("Fumonisin") + stat_regline_equation(label.x=4, label.y=2) 

plot(GhanaFM_linear_dif_bulk)

#Correlate the 2 data points. The correlation coefficient is a number between 1 and -1, The magnitude of the number indicates the strength of the linear relationship. The sign corresponds to the direction of that relationship. A correlation coefficient of -1 indicates a near perfect negatively correlated linear relationship.

cor(GhanaFM$FM_ppm_bulk, GhanaFM$Diference_accept_reject_FM)


#Linear Model to see if prediction is statistically significant

LM_dif_bulk_FM <- lm(GhanaFM$Diference_accept_reject_FM ~ GhanaFM$FM_ppm_bulk)

summary(LM_dif_bulk_FM)


```

#Linear scatterplot Difference and Reject

```{r}
#GhanaFM_linear_dif_reject <- ggplot(data = GhanaFM, aes(FM_ppm_reject, y=Diference_accept_reject_FM)) + geom_point() + geom_smooth(method=lm) + scale_x_continuous("Reject Fumonisin Level (ppm)") + scale_y_continuous("Diference Accept-Reject") + geom_hline(yintercept=0, linetype="dashed", color = "tomato2") + ggtitle("Fumonisin")

#plot(GhanaFM_linear_dif_reject)

#Correlate the 2 data points. The correlation coefficient is a number between 1 and -1, The magnitude of the number indicates the strength of the linear relationship. The sign corresponds to the direction of that relationship. A correlation coefficient of -1 indicates a near perfect negatively correlated linear relationship.

#cor(GhanaFM$FM_ppm_reject, GhanaFM$Diference_accept_reject_FM)


#Linear Model to see if prediction is statistically significant

#LM_dif_reject_FM <- lm(GhanaFM$Diference_accept_reject_FM ~ GhanaFM$FM_ppm_reject)

#summary(LM_dif_reject_FM)


```



#Linear scatterplot Difference and Reject

```{r}
#GhanaFM_linear_dif_accept <- ggplot(data = GhanaFM, aes(FM_ppm_accept, y=Diference_accept_reject_FM)) + geom_point() + geom_smooth(method=lm) + scale_x_continuous("Accept Fumonisin Level (ppm)") + scale_y_continuous("Diference Accept-Reject") + geom_hline(yintercept=0, linetype="dashed", color = "tomato2") + ggtitle("Fumonisin")

#plot(GhanaFM_linear_dif_accept)

#Correlate the 2 data points. The correlation coefficient is a number between 1 and -1, The magnitude of the number indicates the strength of the linear relationship. The sign corresponds to the direction of that relationship. A correlation coefficient of -1 indicates a near perfect negatively correlated linear relationship.

#cor(GhanaFM$FM_ppm_accept, GhanaFM$Diference_accept_reject_FM)


#Linear Model to see if prediction is statistically significant

#LM_dif_accept_FM <- lm(GhanaFM$Diference_accept_reject_FM ~ GhanaFM$FM_ppm_accept)

#summary(LM_dif_accept_FM)


```

#Linear Co-relation  Accept and Reject

```{r}
#Ghana_FM_accept_reject<- ggplot(data = GhanaFM, aes(FM_ppm_accept, y=FM_ppm_reject)) + geom_point() + geom_smooth(method=lm) + scale_x_continuous("Accept Fumonisin Level (ppm)") + scale_y_continuous("Reject Fumonisin Level (ppm)") + geom_abline(intercept = 0, slope = 1, lty=2) + ggtitle("Fumonisin")

#plot(Ghana_FM_accept_reject)

#Correlate the 2 data points. The correlation coefficient is a number between 1 and -1, The magnitude of the number indicates the strength of the linear relationship. The sign corresponds to the direction of that relationship. A correlation coefficient of -1 indicates a near perfect negatively correlated linear relationship.

#cor(GhanaFM$FM_ppm_accept, GhanaFM$FM_ppm_reject)


#Linear Model to see if prediction is statistically significant

#LM_reject_accept_FM <- lm(GhanaFM$FM_ppm_reject ~ GhanaFM$FM_ppm_accept)

#summary(LM_reject_accept_FM)



```

#Linear Co-releation  Mass percentage reject and Fraction Reject FM

```{r}
Ghana_FM_mass_frac<- ggplot(data = GhanaFM, aes(Reject_mass_perc, y=Fraction_reject_FM)) + geom_point() + geom_smooth(method=lm) + scale_x_continuous("Perc Mass Rejected (%)") + scale_y_continuous("Percent Fumonisin removed (%)") + geom_abline(intercept = 0, slope = 1, lty=2) + ggtitle("Fumonisin") + stat_regline_equation(label.x=0.25, label.y=0.6) + stat_cor(aes(label=..rr.label..), label.x=0.25, label.y=0.5)

plot(Ghana_FM_mass_frac)

#Correlate the 2 data points. The correlation coefficient is a number between 1 and -1, The magnitude of the number indicates the strength of the linear relationship. The sign corresponds to the direction of that relationship. A correlation coefficient of -1 indicates a near perfect negatively correlated linear relationship.

cor(GhanaFM$Reject_mass_perc, GhanaFM$Fraction_reject_FM)


#Linear Model to see if prediction is statistically significant

LM_mass_frac_FM <- lm(GhanaFM$Fraction_reject_FM ~ GhanaFM$Reject_mass_perc)

summary(LM_mass_frac_FM)

```
#Boxplot Toxin removed

```{r}
GhanaFM2 <- read.csv("Toxin_percentage_removal_ghana_FM.csv", header = TRUE)

FMfarmstoxinremoval <- ggplot(data = GhanaFM2) + 
  geom_boxplot(aes(x= Sample_type, y= Perc_toxin_removed_FM)) + labs(title = "Percentage of Total Fumonisin Removed by Sorting", x = "Sample Stream", y = "Fumonisin removed in Reject Samples (%)") + theme(legend.position = c(0.2, 0.8)) + coord_cartesian(ylim = c(0, 1)) 

#+ annotate("text", x = 0.6, y = 3, label = paste ("Mean ==", mean_d1), parse = TRUE) + annotate("text", x = 0.6, y = 2.8, label = paste ("Mode ==", mode_d1), parse = TRUE)


plot (FMfarmstoxinremoval)
```


#Boxplot Linear coreleation FM mass (G) vs bulk level FM

```{r}
Ghana_FM_mass_bulk<- ggplot(data = GhanaFM, aes(FM_ppm_bulk, y=Weight_reject)) + geom_point() + geom_smooth(method=lm) + scale_x_continuous("Bulk Fumonisin Level (ppm)") + scale_y_continuous("Mass Removed (g)") +  ggtitle("Fumonisin") + stat_regline_equation(label.x=4, label.y=40)

#add R^2 to plot stat_regline_equation(label.x=4, label.y=2) + stat_cor(aes(label=..rr.label..), label.x=4, label.y=1.5)

plot(Ghana_FM_mass_bulk)

#Correlate the 2 data points. The correlation coefficient is a number between 1 and -1, The magnitude of the number indicates the strength of the linear relationship. The sign corresponds to the direction of that relationship. A correlation coefficient of -1 indicates a near perfect negatively correlated linear relationship.

cor(GhanaFM$FM_ppm_bulk, GhanaFM$Weight_reject)


#Linear Model to see if prediction is statistically significant

LM_mass_bulk_FM <- lm(GhanaFM$Weight_reject ~ GhanaFM$FM_ppm_bulk)

summary(LM_mass_bulk_FM)
```


#Linear co-relation mass rejected vs AF bulk

```{r}
Ghana_FM_mass_bulkAF<- ggplot(data = GhanaFM, aes(AF_ppb_bulk, y=Weight_reject)) + geom_point() + geom_smooth(method=lm) + scale_x_continuous("Bulk Aflatoxin Level (ppb)") + scale_y_continuous("Mass Removed (g)") + ggtitle("Aflatoxin") + stat_regline_equation(label.x=50, label.y=40)


plot(Ghana_FM_mass_bulkAF)

#Correlate the 2 data points. The correlation coefficient is a number between 1 and -1, The magnitude of the number indicates the strength of the linear relationship. The sign corresponds to the direction of that relationship. A correlation coefficient of -1 indicates a near perfect negatively correlated linear relationship.

cor(GhanaFM$AF_ppb_bulk, GhanaFM$Weight_reject)


#Linear Model to see if prediction is statistically significant

LM_mass_bulkAF<- lm(GhanaFM$Weight_reject ~ GhanaFM$AF_ppb_bulk)

summary(LM_mass_bulkAF)
```

